### 2015-08-03 introduction.tex
small tweaks to intro

The Livermore Computing (LC) facility at Lawrence Livermore National Laboratory
(LLNL) supports around 2,500 users on 25 different clusters, ranging
in size from a 1.6 teraflop, 256-core cluster to the
20 petaflop, 1.6 million-core Sequoia machine, currently ranked first and
third on the Graph500~\cite{graph500} and Top500~\cite{top500}
lists, respectively.
%
%The massively parallel simulations that run on LC machines support
%U.S. Department of Energy missions across a range of scientific domains,
%including nuclear physics, material science, climate science, mechanical
%engineering, geophysics, seismology, and stockpile stewardship.
%
The simulation software that runs on these machines is very complex; some
codes depend on specific versions of over 70 dependency libraries.
They require specific compilers, build options and Message Passing Interface (MPI)
implementations to
achieve the best performance, and users may run several
different codes in the same environment as part of larger
scientific workflows.

@@

This paper describes our experiences with the {\it Spack} package manager,
which we have developed at LLNL to manage increasing software complexity.
It makes the following contributions:
\begin{enumerate}
\item A novel, recursive syntax for concisely specifying constraints within
      the large parameter space of HPC packages;
\item A build methodology that ensures packages find their dependencies
      regardless of users' environments;
\item Spack: An implementation of these concepts; and
\item Four use cases detailing LLNL's use of Spack in production.
\end{enumerate}
\noindent
Our use cases highlight Spack's ability to manage complex software.
%
Spack allows users to rapidly compose new package configurations,
manage Python installations, and implement site-specific build policies. 
%
It automates 36 different build configurations of an LLNL
production code with 46 dependencies.
Despite this complexity, Spack's {\it concretization} algorithm
for managing constraints runs in seconds, even for
large packages. Spack's install environment incurs only around
10\% build-time overhead compared to a native install.

>>>>

The Livermore Computing (LC) facility at Lawrence Livermore National Laboratory
(LLNL) supports around 2,500 users on 25 different clusters, ranging
in size from a 1.6 teraflop, 256-core cluster to the
20 petaflop, 1.6 million-core Sequoia machine, currently ranked second on the 
Graph500~\cite{graph500} and third on the Top500~\cite{top500}.
%
%The massively parallel simulations that run on LC machines support
%U.S. Department of Energy missions across a range of scientific domains,
%including nuclear physics, material science, climate science, mechanical
%engineering, geophysics, seismology, and stockpile stewardship.
%
The simulation software that runs on these machines is very complex; some
codes depend on specific versions of over 70 dependency libraries.
They require specific compilers, build options and Message Passing Interface (MPI)
implementations to
achieve the best performance, and users may run several
different codes in the same environment as part of larger
scientific workflows.

@@

This paper describes our experiences with the {\it Spack} package manager,
which we have developed at LLNL to manage increasing software complexity.
It makes the following contributions:
\begin{enumerate}
\item A novel, recursive syntax for concisely specifying constraints within
      the large parameter space of HPC packages;
\item A build methodology that ensures packages find their dependencies
      regardless of users' environments;
\item Spack: An implementation of these concepts; and
\item Four use cases detailing LLNL's use of Spack in production.
\end{enumerate}
\noindent
Our use cases highlight Spack's ability to manage complex software.
%
Spack supports rapid composition of package configurations, management 
of Python installations, and site-specific build policies. 
%
It automates 36 different build configurations of an LLNL
production code with 46 dependencies.
Despite this complexity, Spack's {\it concretization} algorithm
for managing constraints runs in seconds, even for
large packages. Spack's install environment incurs only around
10\% build-time overhead compared to a native install.
